# MERL Workflow {-}

iDE MERL Structure can vary depending on the country and the type of the project.i.e., in Bangladesh the MERL structure is as follows:
**Note:** Here the [p] stands for project based and [i] stands for Institutional. 
Read (#about) for further information.

```{r echo=FALSE}
library(networkD3)
source <- c("Country Director [i]","Country Director [i]",
            "Project Manager [p]","Project Manager [p]",
            "Project Manager [p]", "Project Manager [p]",
            "Manager - MERL [i]", "Manager - MERL [i]")

target <- c("Program Manager [p]","Manager - MERL [i]",
            "Technical Specialist [p] - MERL","Senior Officer-MERL [p]", 
            "Officer - MERL [p]","Assistant - MERL [i]",
            "Technical Spacialist [i] - MERL","Assistant - MERL [i]")

d <- data.frame(source,target)

simpleNetwork(d, Source = "source" , Target = "target", 
              height = NULL, width = NULL,
  linkDistance = 50, charge = -30, fontSize = 7, fontFamily = "serif",
  linkColour = "#666", nodeColour = "#3182bd", opacity = 0.6, zoom = TRUE)


```

# Cross-references {#cross}
Cross-references make it easier for your readers to find and link to elements in your book.

## Chapters and sub-chapters

There are two steps to cross-reference any heading:

1. Label the heading: `# Hello world {#nice-label}`. 
    - Leave the label off if you like the automated heading generated based on your heading title: for example, `# Hello world` = `# Hello world {#hello-world}`.
    - To label an un-numbered heading, use: `# Hello world {-#nice-label}` or `{# Hello world .unnumbered}`.

1. Next, reference the labeled heading anywhere in the text using `\@ref(nice-label)`; for example, please see Chapter \@ref(cross). 
    - If you prefer text as the link instead of a numbered reference use: [any text you want can go here](#cross).

## Captioned figures and tables

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
